---
title: "Final Project Report"
author: "Omkar Purandare"
date: "April 24, 2020"
output: html_notebook
---

# Set Up

```{r}
# load necessary packages
library(tidyverse)
library(mosaic)
library(rvest)
library(tidyr)
library(dplyr)
library(lubridate)
library(DataComputing)
```

# FINAL PROJECT

# Guiding Question

What is the relationship between languages spoken in a country to the respective social and economic development of the country?


## Becoming acquainted with your data sources

The data sources we will be using for this project are divded into 2 categories:

* Primary Data
* Other Data Sources

**Primary Data**

The Primary data soruces we will use are:

* List of Number of languages by country from Wikipedia [(link here)](https://en.wikipedia.org/wiki/Number_of_languages_by_country)

  + This data is found on Wikipedia and it controlled by the Wikimedia Foundation Inc  
  + This data is collected by the Wikimedia Foundation from bunch of sources as the repsective governments webpage, new articles etc. The data is collected for open source knowledge for the population reading this webpage.  
  + This page was last updated on March 27th 2020.
  + The variables I mean to use in thei project are Country or Territory and Established

Heres the data imported into this R notebook
```{r}
# CODE
page <- "https://en.wikipedia.org/wiki/Number_of_languages_by_country"
tableList <- page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)



Languages <- tableList[[1]]
```

Here's a glimpse at the Data Table
```{r}
# CODE
Languages%>% glimpse()
Languages
```


**Other Data Sources**

The Other data soruces we will use are:

* CountryData

  + This data is from the R package DataComputing
  + This data is collected by the Central Intelligence Agency in USA. The data is collected for open source knowledge for the population reading this webpage and thier own cataloging.
  + This page was last updated in 2014.
  + The variables I mean to use in their project are county and GDPgrowth, obesity, netUsers, cell
  
Heres the data imported into this R notebook
```{r}
# CODE
CountryData
```

Here's a glimpse at the Data Table
```{r}
# CODE
CountryData %>% glimpse()
```

## Explore intuition related to the research question

Data Wrangling for Languages 

The renaming of varaibles in the Languages DataFrame
```{r}
# CODE
names(Languages)[c(2,3,4,5,6,7,8,9)] <- c("country", "count_lang","immigrant","total","percent","t", "mean", "median")
```

Since we will only need to be using the number of languages per country information from the Languages DataFrame, we transform the database to accomodate our requirments
```{r}
# CODE
Languages <-
  Languages %>%
  filter(row_number() > 1) %>%
  select(country,count_lang) %>%
  mutate(count_lang = as.numeric(count_lang))
```

**Joining both Datasets** 

Creation of a Hypothesis DataFrame we will use for analysis for the rest of the project by joining the Languages and Country Data DataFrame with the respective identifiers we wish to analyze (eg. GDP growth, netUsers etc.)
```{r}
# CODE
Hypo <-
  Languages %>%
  left_join(CountryData %>% select(country,GDPgrowth, obesity, cell,netUsers), by = c("country" = "country"))

Hypo
```

### Relationship between Languages spoken and GDP Growth

Graphics to show some informative plots and summary statistics to see if there is a relationship between languages spoken in country and growth of countries GDP
```{r}
# CODE
Hypo %>%
  mutate(country = reorder(country, count_lang)) %>%
  ggplot(aes(x=GDPgrowth, y= count_lang)) + stat_smooth() + geom_point()
```

Seing the confidence interval being large we can see there is not much of a relationship between the two varaibles  

### Relationship between Languages spoken and Obesity rate

Graphics to show some informative plots and summary statistics to see if there is a relationship between languages spoken in country and obesity of country
```{r}
# CODE
Hypo %>%
  mutate(country = reorder(country, count_lang)) %>%
  ggplot(aes(x=obesity, y= count_lang)) + stat_smooth() + geom_point()
```

We can see that the higher the languages spoken in country the lower the obesetiy count is for that country 

### Relationship between Languages spoken and Internet Users

Graphics to show some informative plots and summary statistics to see if there is a relationship between languages spoken in country and internet users of country
```{r}
# CODE
Hypo %>%
  mutate(country = reorder(country, count_lang)) %>%
  ggplot(aes(x=netUsers, y= count_lang)) + geom_point() +
  scale_x_log10() +
  stat_smooth(method=loess) 
```

Seing the his grpahich we cans see that countries with more languages spoken have more internet on the general but not drastrically.
