---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 17"
author: "Omkar Purandare"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 17 Exercises: 17.1, 17.3, 17.4, 17.5, 17.7


## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(DataComputing)
library(tidyverse)
library(tidyr)
library(dplyr)
```


## Chapter 17 Exercises

### Problem 17.1

Using the BabyNames data table, find the 10 most popular names according to each of these criteria:

* Boys’ names ending in a vowel.
```{r}
BabyNames %>% 
  filter(grepl( "[aeiou]$", name ) , sex =="M") %>%
  group_by(name, sex) %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total)) %>%
  head(10)
```

* Names with a space (like Lee Ann)
```{r}
BabyNames %>% 
  filter(grepl( "[ ] ", name )) %>%
  group_by(name, sex) %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total))
```

* Names ending with “joe” (like BettyJoe)
```{r}
BabyNames %>% 
  filter(grepl( "joe", name )) %>%
  group_by(name, sex) %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total))
```

### Problem 17.2

Construct a regular expression that matches names that sound like “Caitlin” — A k or c followed by one or more vowels followed by tl then one or more vowels, and ending with n.

```{r}
BabyNames %>% 
  filter(grepl( "^[K,C][a,e,i,o,u]*tl+[a,e,i,o,u]*n$", name ))
```

### Problem 17.3

This regular expression would match to any string regarding a phone number.
The components of the string being extracted is the:  
- 1st 2 numbers   
- A hyphen and the folloing 3 numbers   
- A hyphen and the following 4 numbers   

### Problem 17.4



